\documentclass[a4paper, 14pt, oneside]{Thesis}
% \usepackage{ulem}
\usepackage[square, numbers, comma, sort&compress]{natbib}  % Use the "Natbib" style for the references in the Bibliography
\usepackage{verbatim} 
\usepackage{pslatex} %To set the font as Times New Roman
\usepackage{amsbsy} 
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{amsmath}
\usepackage{latexsym}
\usepackage{amssymb}
\usepackage{epsfig}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{float}
\usepackage{minted}
\usepackage{verbatim} 
\usepackage{epsfig,graphics}
\usepackage{amsmath, amsthm, amssymb}
\usepackage{subfigure}
\usepackage{tikz}
\usepackage{multirow}
\usepackage{multicol}

% TEST CITATION ORDER
% \usepackage[doi=false,isbn=false,url=false,eprint=false,backend=biber, style=authoryear]{biblatex}
% \addbibresource{ref.bib}
% \DeclareSortingNamekeyScheme{
%   \keypart{
%     \namepart{given}
%   }
%   \keypart{
%     \namepart{prefix}
%   }
%   \keypart{
%     \namepart{family}
%   }
%   \keypart{
%     \namepart{suffix}
%   }
% }
% \DeclareNameAlias{sortname}{default}

%\usepackage{fancyhdr}
%\usepackage{lipsum}

%To have 1. instead of [1] in the bibliographic entry
\makeatletter
\renewcommand\@biblabel[1]{#1.}
\makeatother

% To remove hyphenation
\tolerance=1
\emergencystretch=\maxdimen
\hyphenpenalty=10000
\hbadness=10000
%
%----To make sure the page numbers are in the top middle of each page.
\fancypagestyle{Thesis}{
\fancyhf{}
\fancyhead[C]{\thepage}
\%lfoot{\thepage}
\pagestyle{fancy}
}
%redefine the plain pagestyle
%\fancypagestyle{plain}{
%\fancyhf{}
%\fancyhead[C]{\thepage}
%}
%----------------------------------------------------------------------
%% ------------------------s----------------------------------------
\input{bmacros}
\begin{document}

\frontmatter	  % Begin Roman style (i, ii, iii, iv...) page numbering


%  Title Page

\title{ROBUST TRANSFER LEARNING IN DEEP REINFORCEMENT LEARNING}
\authors  {{ SAI PRAKASH   \hspace{0.4in} 185001132\\ \vspace{0.1in}}
{ MAHESH BHARADWAJ K  \hspace{0.4in} 185001089\\\vspace{0.1in}}
{ PRITHAM IMMANUEL ILANGO  \hspace{0.4in} 185001117\\ } }
\addresses  {\\\Computer Science \& Engineering\\}
\date       {June 2022}

\maketitle
%% ----------------------------------------------------------------

\setstretch{1.3}
\fancyhead{}  % Clears all page headers and footers
\rhead{\thepage}  % Sets the right side header to show the page number
\lhead{}  % Clears the left side page header

\pagestyle{fancy}  % Finally, use the "fancy" page style to implement the FancyHdr headers


\Declaration{ 
%
Certified that this project report titled \textbf{``ROBUST TRANSFER LEARNING IN DEEP REINFORCEMENT LEARNING''} is the \textit{bonafide} work of ``\textbf{MAHESH BHARADWAJ K (185001089)}, \textbf{PRITHAM IMMANUEL ILANGO. G (185001117)} and \textbf{SAI PRAKASH (185001132)}, '' who carried out the project work under my supervision.\\
Certified further that to the best of my knowledge the work reported herein does not form part of any other thesis or dissertation on the basis of which a degree or award was conferred on an earlier occasion on this or any other candidate.
  \newlength{\aulength} 
  \settowidth{\aulength}{SSN College of Engineering,}
  \newlength{\auclength} 
  \settowidth{\auclength}{(HEAD OF THE DEPARTMENT)}

\begin{flushleft}
  \parbox[t]{\auclength}{\textbf{DR. T.T. MIRNALINEE}\\
    \textbf{HEAD OF THE
DEPARTMENT}\\    
    Professor,\\
    Department of CSE,\\
    SSN College of Engineering,\\
    Kalavakkam - 603 110}
  \hfill
  \parbox[t]{\aulength}{\textbf{DR. R.S. MILTON}\\
    \textbf{SUPERVISOR}\\
    Professor,\\
    Department of CSE,\\
    SSN College of Engineering,\\
    Kalavakkam - 603 110}
\end{flushleft}
Place:\\
Date:\\

\medskip
Submitted for the examination held on\ldots\ldots\ldots\ldots
\\
\\
\\
{\bf Internal Examiner}\hfill
{\bf External Examiner}
}
\clearpage
%% Abstract in Tamil

% Acknowledgement
%\setstretch{1.3}

\clearpage
%% ----------------------------------------------------------------

% The Abstract Page

\acknowledgements{
We thank GOD, the almighty for giving me strength and knowledge to do this project.

We would like to thank and deep sense of gratitude to our guide \textbf{DR. R.S. MILTON}, Professor, Department of Computer Science and Engineering, for his valuable advice and suggestions as well as his continued guidance, patience and support that helped us to shape and refine our work.

Our sincere thanks to  \textbf{Dr. T.T. MIRNALINEE}, Professor and Head of the Department of Computer Science and Engineering, for her words of advice and encouragement and we would like to thank our project Coordinator \textbf{    Dr.B. BHARATHI}, Associate Professor, Department of Computer Science and Engineering for her valuable suggestions throughout this project.

We express our deep respect to the founder \textbf{Dr. SHIV NADAR}, Chairman, SSN Institutions. We also express our appreciation to our \textbf{Dr. V. E. ANNAMALAI}, Principal, for all the help he has rendered during this course of study.

 We would like to extend our sincere thanks to all the teaching and non-teaching staffs of our department who have contributed directly and indirectly during the course of our project work.
Finally, We would like to thank our parents and friends for their patience, cooperation and moral support throughout my life. 
\newline
\newline
\newline
{\bf MAHESH \space\space\space\space}\hfill {\bf PRITHAM IMMANUEL}\hfill {\bf SAI PRAKASH \space} \newline
{\bf BHARADWAJ K}\hfill {\bf ILANGO}\hfill {\bf \space\space\space\space\space\space\space\space\space\space\space\space\space\space\space\space\space\space\space\space\space\space\space\space\space\space\space\space\space\space\space\space\space\space\space\space\space\space\space\space\space\space\space\space\space\space\space\space\space\space\space\space\space\space\space\space\space\space\space\space\space\space\space}
}
\clearpage  % Abstract ended, start a new page

\addtotoc{ABSTRACT} % Add the "Abstract" page entry to the Contents
\abstract{ \begin{spacing}{2}
Reinforcement Learning is the branch of artificial intelligence where the agent learns by an iterative process of taking actions in its environment and receiving rewards from the environment based on the effect of the actions taken.
Reinforcement learning is particularly useful for simulating use cases which in the real world cannot be experimented with due to the hazardous nature of the experiment such as autonomous driving vehicles.
% The advancement in the practical use of Neural Networks in the recent past has enabled us to use Deep Reinforcement Learning models. In this category of Reinforcement Learning, neural networks are used as function approximators.
Transfer Learning is popular in deep learning as it increases efficiency and reduces training costs. However, transfer learning in reinforcement learning is significantly harder because of the variation in state space of different tasks.
In this paper, we aim to study the effects of adversarial training when implementing transfer learning for reinforcement learning. We hypothesize that better representation learning from adversarial training will enhance transfer learning and make it more viable for reinforcement learning tasks.
We also develop an easy-to-use, customizable  environments in Unity that use the MLagents framework, to train different models.
 We have designed 5 distinct tracks of increasing complexity on which we have trained `cars' to complete a lap successfully using the Proximal Policy Optimization algorithm to perform our experiments.

% We use Unity MLAgents framework to build our own environment to perform our experiments on adversarial robustness of the DRL agents. We have designed 5 distinct tracks of increasing complexity on which we have trained `cars' to complete a lap successfully using the PPO algorithm. 
% Reinforcement Learning typically requires a large amount of time and compute to create an optimised model. This necessitates the need for a robust Transfer Learning technique, which can save time and compute. 
%  RL does not have such a ubiquitous technique for performing Transfer Learning. The training of models in RL is different from DL because we are sampling a dynamic environment, not a static dataset. Therefore, we require a more robust form of TL, which we hypothesize can be achieved by Adverserial Training.
}
\clearpage
%%% DUMMY PAGE FOR TAMIL ABSTRACT WHICH WILL BE PRINTED SEPARATELY
%%% Since LaTeX can't print tamil characters, you've to type tamil 
%%% abstract in some other editors and print it separately. When
%%% binding the thesis place the tamil abstract in place of this blank page
%%% I'm adding this blank page for Table of Contents to point to the right page

%\pagestyle{empty}
%\newpage
%\mbox{}
%\clearpage

\pagestyle{plain}  %The page style headers have been "empty" all this time, now use the "fancy" headers as defined before to bring them back

%% ----------------------------------------------------------------
\lhead{\emph{Contents}}  % Set the left side page header to "Contents"

\tableofcontents % Write out the Table of Contents


%% ----------------------------------------------------------------
\lhead{\emph{List of Tables}}  % Set the left side page header to "List of Tables"
%\begin{spacing}{4}
%\hspace{2.5in} \textbf{List of Tables} \par 
\listoftables
%\end{spacing}

%% ----------------------------------------------------------------
\lhead{\emph{List of Figures}}  % Set the left side page header to "List if Figures"
\listoffigures  % Write out the List of Figures


%2.1 LITERATURE SURVEY OF METAMORPHIC TESTING. . . . . . . . . . . .  13


 % Write out the List of Tables


\mainmatter	  % Begin normal, numeric (1,2,3...) page numbering
\pagestyle{myheadings}  % Return the page headers back to the "fancy" style

\begin{spacing}{1.5}
\input{chapter1} % INTRODUCTION
\input{chapter2} % LITERATURE SURVEY
\input{chapter3} % DESIGN
\input{chapter4} % IMPLEMENTATION
\input{chapter5} % CONCLUSION AND FUTURE WORK
\input{chapter6}
\input{chapter7}
\end{spacing}
\newpage
\appendix
\input{chapter8}
%\addtotoc{REFERENCES}
%\input{References} 

% WORKING REF -DONT DELETE - MAHESH
\bibliographystyle{apalike}
\bibliography{ref}

% TEST REF
% \printbibliography

\end{document}
`
